{{< var titll >}}

### 2024-08-17 index.qmd
abc
abcdef
sommore
manfe
sommorepres
late

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
---

@@

# Testing (latest from Ed's Youtube stream)

## Installling packages

>>>>

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
#webr:
#  show-startup-message: true      # Display status of webR initialization
#  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
#  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
#  cell-options:
#    autorun: true
#filters:
#  - panelize
#  - webr
---

@@

```{r, echo=F}
suppressMessages(ManifoldDestiny::wasmconload()) 
apps <- appn0
adat <- apps[[1]]
amet <- apps[[2]]
cob <- Countinggraphs(adat,selvar=names(adat))
sum(dplyr::select(cob$rdfci,S,T,U,V))
cob$purging(z=amet$prg$z,pri=1) 
cob$plext(2)
sum(dplyr::select(cob$rdfce,S,T,U,V))
def <- Estimation(cob$rdfce)
def$regression("alpha=k0 + k1*g + k2*h")
summary(def$regsum[[1]])
```

```{r}
def$regression("alpha=k0 + k1*g + k2*h")
summary(def$regsum[[1]])
```

```{r}
def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
summary(def$regsum[[1]])
```
